---
title: "Final Project"
author: "Sie Siong Wong - Joe Rovalino - Anil Akyildirim"
date: "11/8/2019"
output: html_document
---

```{r, eval=TRUE}

installed.packages('base64enc')

```

```{r, eval=TRUE}
# Load Requried Packages
library("base64enc")
library("SnowballC")
library("tm")
library("twitteR")
library("syuzhet")
```

```{r, eval=TRUE}

consumer_key <- 'sPwbbZCtf8nfSMxhYTzqI8WHJ'
consumer_secret <- 'KfcOxgElcQ70fi3QNy8LkuDAN18dunXT147MoA8aBOLzpr3Vd3'
access_token <- '600477513-rdd3Fcywq1sfnh5S60egRQxXh0TlDqfrLzyZo4Vk'
access_secret <- 'SdDFCJUOoqAwt671VXeLaD781TdUYdeBSW2gyQMG4P5Zh'

setup_twitter_oauth(consumer_key, consumer_secret, access_token, access_secret)
```

```{r}
tweets <- userTimeline("realDonaldTrump",n=2)
tweets
```
***Delete this later as it is a guide for Python nned to get methods for R ***

https://towardsdatascience.com/trump-tweets-and-trade-96ac157ef082

Can a S&P 500 trading strategy take advantage of President Trump’s trade-related tweets and predict short-term moves in the market? I turned to topic modeling and sentiment analysis to find out. The general project design and workflow is as follows:
1) Data Collection and Preprocessing: raw tweets were collected and preprocessed to pass on tokenized and lemmatized words to the topic model.
2) Topic Modeling with LDA: topic modeling was utilized to assign each tweet a topic. Only tweets related to the trade topic were passed along for sentiment analysis.
3) Sentiment Analysis with VADER: after identifying tweets related to trade, each tweet was assigned a sentiment score. Sentiment scores were passed along as the core input to the trading strategy.
4) Backtesting Trading Strategy on S&P 500 Data: once sentiment scores were assigned, a custom trading strategy was designed to trade on significant sentiment scores.



```{r}
# Load stock data files and Tweets from Trump 
# Step 1 of flows above. 
library(stringr)
#?readLines
snp_raw <- read.csv("sandp.csv", header = TRUE)
typeof(snp_raw)
snp_raw[2,]
tweets_raw <- read.csv("trumptweets.csv", header = TRUE)
typeof(tweets_raw)
tweets_raw[3,]
```

